This group design project has focused on building a downwind faster than the wind (DWFTTW) vehicle. Although the working principles of this type of vehicle are not obvious, this concept has been proven to work on numerous occasions, both theoretically and experimentally. This has been done by multiple reliable sources. One of which is Prof Mark Drela's theoretical analysis of the working principle of the vehicle. Furthermore, a racing competition for this kind of vehicle has been held annually since 2018, in which multiple universities have taken part. The vehicle is composed of a set of wheels connected mechanically to a propeller. As the wind pushes the vehicle and speed builds up, the propeller receives torque from the wheels and propels the vehicle further. This allows the vehicle to reach speeds that can be faster than that of the wind. The theoretical aspect of this will be detailed in the Theory section.

\subsection{Project Inspiration}

Major inspiration for this project came from a YouTube video uploaded by Veritasium (a well-known science and engineering channel) focussed on a DWFTTW vehicle called BlackBird. Its inventors, Rick Cavallaro and John Borton, demonstrated their vehicle on the Ivanpah dry lake bed, south of Las Vegas, and achieved almost three times wind speed. Despite numerous demonstrations of DWFTTW vehicles beating wind-speed, scepticism among the scientific community exists to this day, with the commonly held belief that a vehicle with faster-than-wind capabilities would be a perpetual motion device, violating the first law of thermodynamics. One of the ways to tackle this scepticism is to make such vehicles more widely known by building and demonstrating additional working prototypes.

\subsection{Existing Vehicles}

\textcolor{red}{
    Find any DWFTTW vehicle examples
    Look in detail at the designs and include them in the vehicles section
    Find appropriate pictures of each vehicle
    Read the papers on the DWFTTW vehicles and write literature review on the papers (jean pending)
}

\subsection{Aeolus Competition}

The Aeolus competition is an annual drag race competition for downwind faster than the wind vehicles. The teams collect together and compete for the fastest vehicle. The competition ran in 2018 and 2019 with many teams entering.

We have taken inspiration from this competition in wanting to build a downwind faster than the wind vehicle, with our vehicle being the first iteration for the university competing in this competition.

Although Pam is unmanned, and a smaller scale compared to the maximum limits in the rulebook, the design was thought to be scalable. 

\subsection{Previous Attempts at Downwind-Faster-Than-The-Wind Vehicles}

See Table \ref{tab:prevAttempts}.

%\input{tables/prevAttempts.tex}
% currently located in 2.designSpecs.tex for spatial reasons