\subsection{Project Lifecycle and relevance}

This project is the first iteration of the university building a downwind vehicle. The current project aims to design and manufacture a vehicle that can be tested in at University facilities. There is no previous work on this vehicle in the university and within academia there are still debates as to whether the vehicle is physically possible and what fundamental concepts are at work with the vehicle in motion. A spotlight has been given to this type of vehicle recently due to the Veritasium YouTube video but many academics have rejected the abilities of blackbird to go faster than the wind. We aim to understand the workings of a downwind faster than the wind vehicle and begin an iterative method for projects within the university looking at downwind faster than the wind motion.

\subsection{Project Context}

With the global transportation market moving towards more sustainable forms of travel, all methods for generating thrust to power the future of motion have to be considered. The potentially self-sustaining nature of these vehicles offer significant opportunities for transportation companies to solve the environmental issues that are currently being faced by the planet. The vehicles in discussion are still early in development but a significant input into design could see many aspects of these vehicles implemented into sustainable travel in the future. The mechanical systems involved with these vehicles are not only limited too land vehicles, with boats being able to use these systems for propulsion when travelling. The abilities of these vehicles are promising and could offer significant solutions to the global problem of climate change. The project aims to analyse and discover the potential issues with designing this type of vehicle and give feedback on the limitations of building a vehicle such as this.

\subsection{Project Stakeholders}

See Table \ref{}.

\input{tables/prevAttempts.tex} % From 1.introduction.tex

\input{tables/stakeholders.tex}